Annotation exploration for SCPCP000006, mapping score threshold `r params$mapping_score_thr`

### 2024-10-28 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
update notebook and reports

```{r fig.height=6, fig.width=15, message=FALSE, warning=FALSE, out.width='100%'}
do_Feature_mean( df = cell_type_df_nopass,
                    feature = "ENSG00000081237",
                    group.by = "compartment") +
  ggtitle("PTPRC expression averaged by compartment for cellsthat are not passing the mapping score threshold")
```

>>>>

```{r fig.height=6, fig.width=15, message=FALSE, warning=FALSE, out.width='100%'}
do_Feature_mean( df = cell_type_df_nopass,
                    feature = "ENSG00000081237",
                    group.by = "compartment") +
  ggtitle("PTPRC expression averaged by compartment for cells that are not passing the mapping score threshold")
```
